File-based localization of numerical perturbations in data analysis pipelines

### 2020-08-27 paper.tex
minor fixes

%%%% Commands %%%%
% \newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
% \newcommand{\note}[2]{\color{blue}Note from \textsc{#1}: #2\color{black}}
\newcommand{\revision}[1]{\color{purple}\textbf{REVISION:}#1\color{black}}
\newcommand{\revised}[1]{\color{blue}#1\color{black}\xspace}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\toolname}[0]{Spot\xspace}
\newcommand{\flirt}[0]{\texttt{flirt}\xspace}
\newcommand{\fnirt}[0]{\texttt{fnirt}\xspace}

@@

% \revision{Using the \reprozip trace obtained from CentOS7,
% we captured transient files in CentOS6 and labeled pipeline processes in CentOS7.}
We processed the 20 subjects with PreFreeSurfer and FreeSurfer, using the 2 CentOS versions.
\revised{The PreFreesurfer results obtained in CentOS6 were used as the input of FreeSurfer in both conditions. 
We also used the \reprozip trace file captured in CentOS6 for labeling the processes in both pipelines.}
Each subject was processed twice on the same operating
system to detect within-OS variability coming from pseudo-random
operations. We compared pipeline results using  FreeSurfer tools \texttt{mri\_diff},
\texttt{mris\_diff}, and \texttt{lta\_diff}, to ignore execution-specific information such as file path or
timestamps. To compare segmentations $X$ and $Y$, we used the Dice coefficient defined as follows:
\[DICE=\frac{2|X \cap Y|}{|X| + |Y|}\]

@@

\revised{
\section{Availability of Source Code and Requirements}
\begin{itemize}
  \item Project name: \toolname
  \item Project home page:\url{https://github.com/big-data-lab-team/spot}
  \item Operating system: Linux
  \item Programming language: Python
  \item Other requirements: Python 3.6 or higher, \reprozip, Docker, and Boutiques
  \item License: MIT License
  \item Biotools identifier: \href{https://bio.tools/spottool}{spottool}
  \item SciCrunch ID: \href{https://scicrunch.org/scicrunch/Resources/record/nlx_144509-1/SCR_018915/resolver}{RRID:SCR\_018915}
  \item DOI: \href{https://doi.org/10.5281/zenodo.3873219}{10.5281/zenodo.3873219}

@@

\section{Supplementary Data}
Supplementary materials include Supplementary Table S1. Summary of the subjects used in the experiments.
}

\section{Acknowledgments}

We warmly thank Compute Canada (\url{http://www.computecanada.ca}) and Calcul
Qu\'ebec (\url{http://www.calculquebec.ca}) for providing the infrastructure used in our experiments.
Data and pipelines were provided by the Human Connectome Project, WU-Minn
Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil;
1U54MH091657) funded by the 16 NIH Institutes and Centers that support
the NIH Blueprint for Neuroscience Research; and by the McDonnell
Center for Systems Neuroscience at Washington University.
%\tristan{check ethics}

@@

\includepdf[pages=-]{supplementary-files/subject-details.pdf}

>>>>

%%%% Commands %%%%
% \newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
% \newcommand{\note}[2]{\color{blue}Note from \textsc{#1}: #2\color{black}}
\newcommand{\revised}[1]{\color{blue}#1\color{black}\xspace}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:}#1\color{black}}
\newcommand{\toolname}[0]{Spot\xspace}
\newcommand{\flirt}[0]{\texttt{flirt}\xspace}
\newcommand{\fnirt}[0]{\texttt{fnirt}\xspace}

@@

We processed the 20 subjects with PreFreeSurfer and FreeSurfer, using the 2 CentOS versions.
\revised{The PreFreesurfer results obtained in CentOS6 were used as the input of FreeSurfer in both conditions. 
We also used the \reprozip trace file captured in CentOS6 for labeling the processes in both pipelines.}
Each subject was processed twice on the same operating
system to detect within-OS variability coming from pseudo-random
operations. We compared pipeline results using  FreeSurfer tools \texttt{mri\_diff},
\texttt{mris\_diff}, and \texttt{lta\_diff}, to ignore execution-specific information such as file path or
timestamps. To compare segmentations $X$ and $Y$, we used the Dice coefficient defined as follows:
\[DICE=\frac{2|X \cap Y|}{|X| + |Y|}\]

@@

\revised{
\section{Availability of Source Code and Requirements}
\begin{itemize}
  \item Project name: \toolname
  \item Project home page: \url{https://github.com/big-data-lab-team/spot}
  \item Operating system: Linux
  \item Programming language: Python (3.6 or higher)
  \item Main dependencies: \reprozip, Docker, and Boutiques
  \item Other dependencies: see \href{https://github.com/big-data-lab-team/spot}{\texttt{setup.py}}
  \item License: MIT License
  \item Biotools identifier: \href{https://bio.tools/spottool}{spottool}
  \item SciCrunch ID: \href{https://scicrunch.org/scicrunch/Resources/record/nlx_144509-1/SCR_018915/resolver}{RRID:SCR\_018915}
  \item DOI: \href{https://doi.org/10.5281/zenodo.3873219}{10.5281/zenodo.3873219}

@@

\section{Supplementary Data}
Supplementary materials include Supplementary Table S1 that contains a summary of the subjects used in the experiments.
}

\section{Acknowledgments}
\revised{We thank the reviewers for their thorough and insightul review which greatly contributed to the improvement 
of the paper.}
We warmly thank Compute Canada (\url{http://www.computecanada.ca}) and Calcul
Qu\'ebec (\url{http://www.calculquebec.ca}) for providing the infrastructure used in our experiments.
Data and pipelines were provided by the Human Connectome Project, WU-Minn
Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil;
1U54MH091657) funded by the 16 NIH Institutes and Centers that support
the NIH Blueprint for Neuroscience Research; and by the McDonnell
Center for Systems Neuroscience at Washington University.
%\tristan{check ethics}

@@

\includepdf[pages=-]{supplementary-files/file1.pdf}
